\input{cv_header.tex}

\begin{document}

\begin{center}
\Large{\bf My Name}      % make the name stand out
\end{center}

\begin{center}
MAE Department Box 5725\\
Clarkson University\\
Potsdam, NY 13699-5725\\
(315) 268-2204\\
\em{myemail@clarkson.edu}
\end{center}

\section*{EDUCATION}
{\bf Some University} \hspace*{\fill}
{ Some Place, XX}
\par
{\em January 19XX - November 1997}
\par
Doctoral degree in the Mechanical and Aerospace Engineering program,
with concentration in the areas of blah blah.  Master of Arts degree received June 1994.  Advisor: Professor D. D. Dummy.
\par
\vspace{\baselineskip}
{\bf University of Somewhere} \hspace*{\fill}
{ Somewhere, SN}
\par
{\em September 1987 - June 1991}
\par
Bachelor of Science degree in Mechanical Engineering.   
Undergraduate research advisor: Professor Somebody.  Research topic: something.

\section*{EXPERIENCE}
{\bf Clarkson University}  \hspace*{\fill} Potsdam, NY
\par
{\em Associate Professor, Mechanical and Aeronautical Eng. Dept.} \hfill {\em March 2006 -May 2013}\\
{\em Assistant Professor, Mechanical and Aeronautical Eng. Dept.} \hfill {\em January 2001 - March 2006 }\\
{\em Courtesy Appointment, Math. and Computer Science Dept.} 

\par
Current research is on doing fun stuff.  

\par
\vspace{\baselineskip}
{\bf Another place I have been}  \hspace*{\fill} City, ST
\par
{\em Title goes here} \hfill {\em September 2008 - July 2009}
\par
Did a bunch of stuff. Host: D.\ D.\ Dummy 

% The vbox command makes sure this doesn't get broken between pages
\vbox{
\section*{PROFESSIONAL MEMBERSHIPS}
American Society of Mechanical Engineers (ASME) \\
American Society of Engineering Education (ASEE) \\
}

\input{cv_tables.tex}

\end{document}

